SNIK: Textbook Knowledge on Hospital Information Management as Linked Data

### 2021-11-21 paper.tex
Finished alpha version and shortened to exactly 7 pages.

%\pretitle{}
\title{SNIK: Textbook Knowledge on Hospital Information Management as Linked Data}
%\runningtitle{The SNIK Ontology of Hospital Information Management}
%\subtitle{}
\iffalse
% Two or more authors:
\author[A]{\inits {K.}\fnms{Konrad} \snm{Höffner}\ead[label=e1]{konrad.hoeffner@imise.uni-leipzig.de}%
\thanks{Corresponding author. \printead{e1}.}},
\author[A]{\fnms{Franziska} \snm{Jahn}\ead[label=e2]{franziska.jahn@imise.uni-leipzig.de}},
\author[A]{\fnms{Birgit} \snm{Schneider}\ead[label=e3]{birgit.schneider@imise.uni-leipzig.de}},
%\author[A]{\fnms{Anna} \snm{Lörke}\ead[label=e4]{anna.loerke@imise.uni-leipzig.de}},
\author[A]{\fnms{Thomas} \snm{Pause}\ead[label=e5]{thomas.pause@imise.uni-leipzig.de}},
\author[A]{\fnms{Alfred} \snm{Winter}\ead[label=e6]{alfred.winter@imise.uni-leipzig.de}}
%\runauthor{K. Höffner et al.}
\address[A]{Institute for Medical Informatics, Statistics and Epidemiology (IMISE),
\orgname{University of Leipzig}, \cny{Germany}\printead[presep={\\}]{e1,e2,e3,e5,e6}}
%Medical Informatics, Management of Health Information Systemsi
%Härtelstraße 16--18, D-04107 Leipzig
\fi

\author{\IEEEauthorblockN{Konrad Höffner}
\IEEEauthorblockA{\textit{Institute for Medical Informatics, Statistics and Epidemiology} \\
\textit{Leipzig University}\\
Leipzig, Germany \\
\url{https://orcid.org/0000-0001-7358-3217}}
\and
\IEEEauthorblockN{Franziska Jahn}
\IEEEauthorblockA{\textit{Institute for Medical Informatics, Statistics and Epidemiology} \\
\textit{Leipzig University}\\
Leipzig, Germany \\
\url{https://orcid.org/0000-0002-7687-8544}}
\and
\and
\IEEEauthorblockN{Alfred Winter}
\IEEEauthorblockA{\textit{Institute for Medical Informatics, Statistics and Epidemiology} \\
\textit{Leipzig University}\\
Leipzig, Germany \\
%alfred.winter@imise.uni-leipzig.de}
\url{https://orcid.org/0000-0003-0179-954X}}
\and
\IEEEauthorblockN{Thomas Pause}
\IEEEauthorblockA{\textit{Institute for Medical Informatics, Statistics and Epidemiology} \\
\textit{Leipzig University}\\
Leipzig, Germany \\
\url{https://orcid.org/0000-0001-5832-4890}}
}
\maketitle
\begin{abstract}
%Textbooks contain abstract knowledge about a domain.
Textbooks about information management in hospitals describe the planning, monitoring and directing of a hospital's information system.
SNIK consists of the manually transformed content of three such textbooks as Linked Open Data.
The data model describes information management functions, roles executing these functions and the information used or updated by these functions.
%SNIK provides applications that are used to teach students internationally.
%and the result of applying the data model to three textbooks, an interview and a standard.
%To compare, 
%, making it a natural fit for RDF, RDFS and OWL.
%As the domain is large and highly relevant to students of Medical Informatics, modelling the knowledge is not only possible but also very useful.
We publish the result over several different interfaces that are useful for researchers, information system administrators or students, depending on their objectives and their capabilities.
\end{abstract}

@@

% ICSCR style
\begin{IEEEkeywords}
linked open data visualization,health information systems,information management
\end{IEEEkeywords}
%\end{frontmatter}

\section{Introduction}
A health information system (HIS) is the socio-technical subsystem of a care delivery organization~\citep{bb}.
This includes its different application systems, computers, and network components as well as their users.
A HIS processes data, information, and knowledge and its management involves planning, monitoring and directing of those activities.
Due to the complexity and the unique conditions in health care, HIS management is an challenging task.
There are many different frameworks, textbooks and articles describing the scope of HIS management from the perspective of medical informatics.
%However, the disciplines of business informatics and information systems (IS) provide an even broader view on information systems and their management.
%A structured representation of the different perspectives leads to a holistic view on HIS management and helps help researchers and students connect their existing knowledge with further knowledge from other sources during research and learning.
In order to integrate different knowledge sources and to provide the knowledge in a structured, machine-readable data format, we extracted knowledge about HIS management from three textbooks~\citep{bb,ob,he} and other sources, see \cref{tab:source}.
The combination of this knowledge~\citep{semantischesnetz,domaene,approachtosupport} results in SNIK, the Semantic Network of Information Management in Hospitals (\enquote{Krankenhaus} in German).

@@

%As the domain is large and highly relevant to students of Medical Informatics, modelling the knowledge is not only possible but also very useful.
Medical informatics students, who are trained for executive positions in information management departments of healthcare institutions, such as hospitals, need a clear terminology of their domain.
Due to different frameworks and textbooks dealing with information management in healthcare, modelling the knowledge unravels the links between the different views on information management.
These are only implicitly known or not known at all by experts in the field.

We present a common data model for the domain and the result of applying the data model to three textbooks.
We publish the result over several interfaces that are useful for researchers, practitioners and students, depending on their objectives and their Semantic Web skills.

Publishing textbook knowledge as Linked Data enables different ways of teaching.
%The data is continously revised: users constantly report wrong or missing data in the visualization, which is then corrected, respectively revised, by the researchers of the project.

@@

\section{Data Model}
In order to specify, which information should be extracted from the books and to facilitate comparisons, we use a common data model.
Because processed textbooks contain abstract knowledge instead of information about any specific hospital, all concepts are modelled as classes.
We thus call our data model the \enquote{meta model} in accordance with the term's definition as a shared modelling language~\citep[p.~8]{ob}.
The meta model (see \cref{fig:metamodel}) provides a common vocabulary for the domain of HIS management and thus defines, which superclasses and property can be used.
SNIK version \snikversion{} comprises five subontologies that are built upon the meta model, see Table 1.
At the head of the class hierarchy (see \cref{fig:hierarchy}) is the \enquote{Top} class, which has exactly three disjunctive subclasses.

Following the meta model, each class has to be a subclass of exactly one of them.
The correct superclass of a new concept can be found by answering the question: Who (\enquote{Role}) does what (\enquote{Function}) and which information (\enquote{EntityType}) is needed? If a concept is neither of them, it cannot be modeled using the meta model.
As the subclass relation is transitive, a new class can be placed further down the hierarchy and it can still be inferred, whether it is a Function, Role or EntityType (see Figure 3).
Besides the subclass relationship, two classes can be connected with relations provided by the meta model.
The generic \enquote{is associated with} relationship carries little information.
For example, a role and a function can be connected as \enquote{is involved in} \enquote{is responsible for} and \enquote{approves}.
Relations that are neither of them can either be modeled by using the generic \enquote{is associated with} relation or by creating and using a new sub relation of \enquote{is associated with}

As a concession to practicality, we express each geleral rule extracted from a textbook as a single triple using classes as subject and object, and a property of the meta model.
For example, the rule "the CEO is involved in project reviews" is modelled as \enquote{\texttt{:Ceo} \aurl{meta}{isInvolvedIn} \texttt{:ProjectReview}.}, where \texttt{:Ceo} is a subclass of \aurl{meta}{Role} and \aurl{meta}{ProjectReview} is a subclass of \aurl{meta}{Function}.
While an OWL restrictions using \aurl{owl}{someValuesFrom} and \aurl{owl}{allValuesFrom} would be technically correct, the knowledge is not expressed that specifically in the textbooks.
Additionally, encoding each fact as a single triple facilitates tool support and prevents inconsistencies through non-atomic changes.

\paragraph{}

@@

\begin{table}
\caption{Access Options and Details.%
%KBox usage example: \texttt{pip install kbox \&\& kbox -kb http://www.snik.eu/ontology -install -server}.%doesn't work right now
}
\label{tab:access}
\begin{tabulary}{\columnwidth}{lL}
\toprule
URL						&\url{http://www.snik.eu/ontology}\\
Version					&\snikversion{}\\
License					&CC BY-NC-SA 4.0\\
Ontology Documentation	&\url{https://snikproject.github.io/ontology/}\\
SPARQL Endpoint			&\url{http://www.snik.eu/sparql}\\
LOD Cloud				&\url{https://lod-cloud.net/dataset/snik}\\
%Datahub				&\url{https://datahub.io/imise/snik/v/1}\\%offline
%Docker
KBox~\cite{kbox} Graph	&\url{http://www.snik.eu/ontology}\\
RDF Browser				&\url{http://www.snik.eu/ontology}\\
Visualization			&\url{http://www.snik.eu/graph}\\
Download				&\url{https://github.com/snikproject/ontology/archive/refs/tags/\snikversion.zip}\\
Figshare				&\url{https://doi.org/10.6084/m9.figshare.17057084.v1}\\
\bottomrule
\end{tabulary}%The source code for the services is available at \url{https://github.com/imise}
\end{table}

\begin{table}
\caption{Statistics}
\label{tab:statistics}
\centering
\begin{tabulary}{\columnwidth}{lS}
\toprule
\textbf{Category}					&\textbf{Count}\\
\midrule
Triples								&\sniktriples{}\\
Classes								&\snikclasses{}\\
Properties							&\snikproperties{}\\
Internal Links						&360\\
Links to HITO  						&260\\
Links to DBpedia~\citep{dbpedia} 	&\sniklinks{}\\
%Subontologies	&\url{http://www.snik.eu/ontology/bb}\\
%		&\url{http://www.snik.eu/ontology/ciox,}\\
%		&\url{http://www.snik.eu/ontology/ob}\\
%		&\url{http://www.snik.eu/ontology/he}\\
%		&\url{http://www.snik.eu/ontology/it4it}\\
\bottomrule
\end{tabulary}%The source code for the services is available at \url{https://github.com/imise}
\end{table}

\begin{figure*}
\caption{The SNIK meta model}
\label{fig:metamodel}
\centering
\includegraphics[width=\textwidth]{img/metamodel9s.pdf}
\end{figure*}

\section{Sources}\label{sec:sources}
Three textbooks provide different views on the domain of Hospital Information Management:
\citet{bb} presents a broad view on \enquote{typical architectures of health information systems and their systematic strategic management}.
\citep{ob} concentrates on the \emph{tactical} management of information systems in general and on healthcare in particular.
The focus of tactical management lies on the planning and operation of projects.
\citet{he} explains information management beyond the scope of healthcare.
Other sources are interviews and standards.
%CIOX is based on an interview with the CIO of the Universitätsklinikum Leipzig.
%IT4IT is based on the IT4IT standard.\todo{Sebastian: Was über Standards und IT4IT schreiben}

@@

\begin{enumerate}[align=left, labelwidth=1ex]
\item The first ring consists of the given role and all roles that are connected by a path of \aurl{rdfs}{subClassOf} and \aurl{skos}{closeMatch} edges.
\item The function ring consists of all functions adjacent to roles in the inner ring.
\item The third ring consists of all entity types adjacent to functions in the middle ring.
\item The final ring consists of all entity types that are connected to entity types from the third ring by a path of \aurl{skos}{closeMatch} and reverse \aurl{rdfs}{subClassOf} edges.
\end{enumerate}
\begin{figure}[h!]
    \centering
    \includegraphics[width=\columnwidth]{img/class-use-project-manager.pdf}
    \caption{\emph{Role Use} of \aurl{bb}{ProjectManager}. Outermost layer ommitted due to space limitiations.}\label{fig:classuse}
\end{figure}

@@

\subsection{Neighbourhood Operations}
Exploration using neighbours, that is the successive uncovering of nodes adjacent to a starting node given by a user, is a common feature of tools such as \cite{lodlive} and \cite{vizlod}.%
\subsection{Star}
The directed and undirected star operations show nodes connected to selected nodes via all paths that contain at most one property other than \aurl{skos}{closeMatch}.
The \emph{circle star} also rearranges the nodes using the force-directed layout locally on the currently visible subgraph.
\Cref{fig:star} shows a mind map of strategic information management, created by an undirected star, which can be used by a teacher to prepare a lecture about the topic.
\begin{figure}[h!]
    \centering
    \includegraphics[width=\columnwidth]{img/strategic-im.pdf}
    \caption{Undirected \emph{Star} of \aurl{bb}{StrategicInformationManagement}.}
	\label{fig:star}
\end{figure}
\vspace{-3pt}

@@

The DBpedia-powered Clover Quiz~\citep{cloverquiz} shows that ontologies can be used to automatically generate multiple-choice questions.
We apply this approach to SNIK and generate 1231 English questions using the templates described in \cref{tab:templates}.
It was used by students from the Universities of Amsterdam, Heidelberg and Leipzig during the international Frank van Swieten lectures in 2019.
To provide difficult wrong answers, the so called \emph{distractors}, we use direct neighbours of the classes that represent the correct answers.
Due to the limited nesting capabilties of SPARQL, which does not support loops but only subqueries that cannot access variables declared outside their scope, querying for distinct sets of 4 neighbours, where exactly one was connected over a certain property to a certain object, was not possible with our Virtuoso SPARQL endpoint initially.
We circumvented the timeout by calculating the neighbour-relation as a first step and uploading it to the endpoint.

%SNIK Quiz is freely available as an open source web application.
Because SNIK only contains the knowledge that the source textbooks describe, it does not contain the complete domain of Hospital Information Management.
As such, negative questions are problematic, as the given relationship could hold in the real world but not be described in the textbook source of the class.
The same problem concerns the distractors of positive questions.
So this problem cannot be avoided.
However, this is one of the reasons that we don't ask count questions like \enquote{How many functions is the CIO responsible for?}, which don't help much for learning anyways. % improve writing
Relationships could also hold implicitly through the subclass hierarchy.
For example, \aurl{bb}{ChiefInformationOfficer} is a subclass of \aurl{bb}{InformationManagementStaff}, which is responsible for \aurl{bb}{OperationalInformationManagement}.
It is unclear, whether the CIO is also responsible for operational information management.
An ongoing bachelor's thesis~\citep{snikquiz} is investigating different strategies of generating complex questions, answers and distrators.

@@

\section{Acknowledgments}
This work is supported by the DFG (German Research Foundation) under the Projects SNIK, grant no. 1605/7-1 and 1387/8-1, as well as HITO, grant no. WI 1605/11-1 and I3726-N31.
%We thank the publishers ... and ... for granting us permission to publish the subontologies based on the textbooks \citet{bb,ob,he} under an open license.
%\nocite{*} 
\todo{FJ: Hmmm, ziemlich selbstreferenziell. Brauchen wir da wirklich so viele Publikationen von uns? Welche anderen könnte man noch einbringen? Ich schaue auch mal, was mir so über den Weg läuft.}
%\bibliographystyle{ios1}
\bibliographystyle{IEEEtran}
\bibliography{paper,snik,relatedwork}
%\section{Notes to Reviewers}
%This paper includes and extends text and figures from:
%\citet{snikgraph}
%\todo{KH: Extending a poster should be allowed for a journal but maybe not for a conference. replace text and figures from the poster. should only be the snik graph chapter. use snik graph paper instead.}
%Update: All the text from the paper should now be commented out or properly referenced.
\end{document}

>>>>

%\pretitle{}
\title{SNIK: Textbook Knowledge on Hospital Information Management as Linked Data}
%\thanks{This work is supported by the DFG (German Research Foundation) under the Project SNIK, Grant no. 1605/7-1 and 1387/8-1.}%bug: will create an empty first page
%\runningtitle{The SNIK Ontology of Hospital Information Management}
%\subtitle{}
\iffalse
% Two or more authors:
\author[A]{\inits {K.}\fnms{Konrad} \snm{Höffner}\ead[label=e1]{konrad.hoeffner@imise.uni-leipzig.de}%
\thanks{Corresponding author. \printead{e1}.}},
\author[A]{\fnms{Franziska} \snm{Jahn}\ead[label=e2]{franziska.jahn@imise.uni-leipzig.de}},
\author[A]{\fnms{Birgit} \snm{Schneider}\ead[label=e3]{birgit.schneider@imise.uni-leipzig.de}},
%\author[A]{\fnms{Anna} \snm{Lörke}\ead[label=e4]{anna.loerke@imise.uni-leipzig.de}},
\author[A]{\fnms{Thomas} \snm{Pause}\ead[label=e5]{thomas.pause@imise.uni-leipzig.de}},
\author[A]{\fnms{Alfred} \snm{Winter}\ead[label=e6]{alfred.winter@imise.uni-leipzig.de}}
%\runauthor{K. Höffner et al.}
\address[A]{Institute for Medical Informatics, Statistics and Epidemiology (IMISE),
\orgname{University of Leipzig}, \cny{Germany}\printead[presep={\\}]{e1,e2,e3,e5,e6}}
%Medical Informatics, Management of Health Information Systemsi
%Härtelstraße 16--18, D-04107 Leipzig
\fi

\author{\IEEEauthorblockN{Konrad Höffner}
\IEEEauthorblockA{\textit{Institute for Medical Informatics, Statistics and Epidemiology} \\
\textit{Leipzig University}\\
Leipzig, Germany \\
\url{https://orcid.org/0000-0001-7358-3217}}
\and
\IEEEauthorblockN{Franziska Jahn}
\IEEEauthorblockA{\textit{Institute for Medical Informatics, Statistics and Epidemiology} \\
\textit{Leipzig University}\\
Leipzig, Germany \\
\url{https://orcid.org/0000-0002-7687-8544}}
\and
\and
\IEEEauthorblockN{Alfred Winter}
\IEEEauthorblockA{\textit{Institute for Medical Informatics, Statistics and Epidemiology} \\
\textit{Leipzig University}\\
Leipzig, Germany \\
%alfred.winter@imise.uni-leipzig.de}
\url{https://orcid.org/0000-0003-0179-954X}}
\and
\IEEEauthorblockN{Thomas Pause}
\IEEEauthorblockA{\textit{Institute for Medical Informatics, Statistics and Epidemiology} \\
\textit{Leipzig University}\\
Leipzig, Germany \\
\url{https://orcid.org/0000-0001-5832-4890}}
}
\maketitle
\begin{abstract}
%Textbooks contain abstract knowledge about a domain.
Textbooks about information management in hospitals describe the planning, monitoring and directing of a hospital's information system.
SNIK consists of the manually transformed content of three such textbooks as Linked Open Data.
The data model describes information management functions, roles executing these functions and the information used or updated by these functions.
%SNIK provides applications that are used to teach students internationally.
%and the result of applying the data model to three textbooks, an interview and a standard.
%To compare, 
%, making it a natural fit for RDF, RDFS and OWL.
%As the domain is large and highly relevant to students of Medical Informatics, modelling the knowledge is not only possible but also very useful.
We publish the result over several interfaces that are useful for researchers, administrators or students, depending on their objectives and capabilities.
\end{abstract}

@@

% ICSCR style
\begin{IEEEkeywords}
linked open data, information management
\end{IEEEkeywords}
%\end{frontmatter}

\section{Introduction}
A health information system (HIS) is the socio-technical subsystem of a care delivery organization~\citep{bb}.
This includes its different application systems, computers, and network components as well as their users.
A HIS processes data, information, and knowledge and its management involves planning, monitoring and directing of those activities.
Due to the complexity and the unique conditions in health care, HIS management is an challenging task.
There are many different frameworks, textbooks and articles describing the scope of HIS management from the perspective of medical informatics.
%However, the disciplines of business informatics and information systems (IS) provide an even broader view on information systems and their management.
%A structured representation of the different perspectives leads to a holistic view on HIS management and helps help researchers and students connect their existing knowledge with further knowledge from other sources during research and learning.
In order to integrate different knowledge sources and to provide the knowledge in a structured, machine-readable data format, we extracted knowledge about HIS management from several sources, see \cref{tab:source}.
%three textbooks~\citep{bb,ob,he} and other sources, see \cref{tab:source}.
%\section{Sources}\label{sec:sources}
Three textbooks provide different views on the domain of Hospital Information Management:
\citet{bb} presents a broad view on \enquote{typical architectures of health information systems and their systematic strategic management}.
\citep{ob} concentrates on the \emph{tactical} management of information systems in general and on healthcare in particular.
The focus of tactical management lies on the planning and operation of projects.
\citet{he} explains information management beyond the scope of healthcare.
Other sources are interviews and standards.
%CIOX is based on an interview with the CIO of the Universitätsklinikum Leipzig.
%IT4IT is based on the IT4IT standard.\todo{Sebastian: Was über Standards und IT4IT schreiben}

The combination of this knowledge~\citep{semantischesnetz,domaene,approachtosupport} results in SNIK, the Semantic Network of Information Management in Hospitals (\enquote{Krankenhaus} in German).

@@

%As the domain is large and highly relevant to students of Medical Informatics, modelling the knowledge is not only possible but also very useful.
Medical informatics students, who are trained for executive positions in information management departments of healthcare institutions, such as hospitals, need a clear terminology of their domain.
Due to different frameworks and textbooks dealing with information management in healthcare, modelling the knowledge unravels the links between the different views on information management.
These are only implicitly known or not known at all by experts in the field.
%
We present a common data model for the domain and the result of applying the data model to three textbooks.
We publish the result over several interfaces that are useful for researchers, practitioners and students, depending on their objectives and their Semantic Web skills.
%
Publishing textbook knowledge as Linked Data enables different ways of teaching.
%The data is continously revised: users constantly report wrong or missing data in the visualization, which is then corrected, respectively revised, by the researchers of the project.

@@

\section{Data Model}
In order to specify, which information should be extracted from the books and to facilitate comparisons, we use a common data model.
Because processed textbooks contain abstract knowledge instead of information about any specific hospital, all concepts are modelled as classes.
We thus call our data model the \enquote{meta model} in accordance with the term's definition as a shared modelling language~\citep[p.~8]{ob}.
The meta model (see \cref{fig:metamodel}) provides a common vocabulary for the domain of HIS management and thus defines, which superclasses and property can be used.
SNIK version \snikversion{} comprises five subontologies that are built upon the meta model, see Table 1.
At the head of the class hierarchy (see \cref{fig:hierarchy}) is the \enquote{Top} class, which has exactly three disjunctive subclasses.
%
Following the meta model, each class has to be a subclass of exactly one of them.
The correct superclass of a new concept can be found by answering the question: Who (\enquote{Role}) does what (\enquote{Function}) and which information (\enquote{EntityType}) is needed? If a concept is neither of them, it cannot be modeled using the meta model.
As the subclass relation is transitive, a new class can be placed further down the hierarchy and it can still be inferred, whether it is a Function, Role or EntityType (see Figure 3).
Besides the subclass relationship, two classes can be connected with relations provided by the meta model.
The generic \enquote{is associated with} relationship carries little information.
For example, a role and a function can be connected as \enquote{is involved in} \enquote{is responsible for} and \enquote{approves}.
Relations that are neither of them can either be modeled by using the generic \enquote{is associated with} relation or by creating and using a new sub relation of \enquote{is associated with}
%
As a concession to practicality, we express each geleral rule extracted from a textbook as a single triple using classes as subject and object, and a property of the meta model.
For example, the rule "the CEO is involved in project reviews" is modelled as \enquote{\texttt{:Ceo} \aurl{meta}{isInvolvedIn} \texttt{:ProjectReview}.}, where \texttt{:Ceo} is a subclass of \aurl{meta}{Role} and \aurl{meta}{ProjectReview} is a subclass of \aurl{meta}{Function}.
While an OWL restrictions using \aurl{owl}{someValuesFrom} and \aurl{owl}{allValuesFrom} would be technically correct, the knowledge is not expressed that specifically in the textbooks.
Additionally, encoding each fact as a single triple facilitates tool support and prevents inconsistencies through non-atomic changes.

@@

\begin{table}
\caption{Access Options and Details.%
%KBox usage example: \texttt{pip install kbox \&\& kbox -kb http://www.snik.eu/ontology -install -server}.%doesn't work right now
}
\label{tab:access}
\begin{tabulary}{\columnwidth}{lL}
\toprule
URL						&\url{http://www.snik.eu/ontology}\\
Version					&\snikversion{}\\
License					&CC BY-NC-SA 4.0\\
Documentation	&\url{https://snikproject.github.io/ontology/}\\
SPARQL Endpoint			&\url{http://www.snik.eu/sparql}\\
LOD Cloud				&\url{https://lod-cloud.net/dataset/snik}\\
%Datahub				&\url{https://datahub.io/imise/snik/v/1}\\%offline
%Docker
KBox~\cite{kbox} Graph	&\url{http://www.snik.eu/ontology}\\
RDF Browser				&\url{http://www.snik.eu/ontology}\\
Visualization			&\url{http://www.snik.eu/graph}\\
Download				&\url{https://github.com/snikproject/ontology/archive/refs/tags/\snikversion.zip}\\
Figshare				&\url{https://doi.org/10.6084/m9.figshare.17057084.v1}\\
\bottomrule
\end{tabulary}%The source code for the services is available at \url{https://github.com/imise}
\end{table}

\begin{table}
\caption{Statistics}
\label{tab:statistics}
\centering
\begin{tabulary}{\columnwidth}{lS}
\toprule
\textbf{Category}					&\textbf{Count}\\
\midrule
Triples								&\sniktriples{}\\
Classes								&\snikclasses{}\\
Properties							&\snikproperties{}\\
Internal Links						&360\\
Links to HITO~\citep{hitometh2}  	&260\\
Links to DBpedia~\citep{dbpedia} 	&\sniklinks{}\\
%Subontologies	&\url{http://www.snik.eu/ontology/bb}\\
%		&\url{http://www.snik.eu/ontology/ciox,}\\
%		&\url{http://www.snik.eu/ontology/ob}\\
%		&\url{http://www.snik.eu/ontology/he}\\
%		&\url{http://www.snik.eu/ontology/it4it}\\
\bottomrule
\end{tabulary}%The source code for the services is available at \url{https://github.com/imise}
\end{table}

\begin{figure*}
\caption{The SNIK meta model}
\label{fig:metamodel}
\centering
\includegraphics[width=0.9\textwidth]{img/metamodel9s.pdf}
%\includegraphics[width=\textwidth]{img/metamodel9s.pdf}
\end{figure*}

@@

\begin{enumerate}%[align=left, labelwidth=1ex]
\item The first ring consists of the given role and all roles that are connected by a path of \aurl{rdfs}{subClassOf} and \aurl{skos}{closeMatch} edges.
\item The function ring consists of all functions adjacent to roles in the inner ring.
\item The third ring consists of all entity types adjacent to functions in the middle ring.
\item The final ring consists of all entity types that are connected to entity types from the third ring by a path of \aurl{skos}{closeMatch} and reverse \aurl{rdfs}{subClassOf} edges.
\end{enumerate}
\begin{figure}[h!]
    \centering
    \includegraphics[width=\columnwidth]{img/class-use-project-manager.pdf}
    \caption{\emph{Role Use} of \aurl{bb}{ProjectManager}. Outermost layer ommitted due to space limitiations.}\label{fig:classuse}
\end{figure}

@@

\paragraph{Neighbourhood Operations}
Exploration using neighbours, that is the successive uncovering of nodes adjacent to a starting node given by a user, is a common feature of tools such as \cite{lodlive} and \cite{vizlod}.%
\paragraph{Star}
The directed and undirected star operations show nodes connected to selected nodes via all paths that contain at most one property other than \aurl{skos}{closeMatch}.
The \emph{circle star} also rearranges the nodes using the force-directed layout locally on the currently visible subgraph.
\Cref{fig:star} shows a mind map of strategic information management, created by an undirected star, which can be used by a teacher to prepare a lecture about the topic.
\begin{figure}[h!]
    \centering
    \includegraphics[width=\columnwidth]{img/strategic-im.pdf}
    \caption{Undirected \emph{Star} of \aurl{bb}{StrategicInformationManagement}.}
	\label{fig:star}
\end{figure}
\vspace{-3pt}

@@

The DBpedia-powered Clover Quiz~\citep{cloverquiz} shows that ontologies can be used to automatically generate multiple-choice questions.
We apply this approach to SNIK and generate 1231 English questions using the templates described in \cref{tab:templates}.
It was used by students from the Universities of Amsterdam, Heidelberg and Leipzig during the international Frank van Swieten lectures in 2019.
To provide difficult wrong answers, the so called \emph{distractors}, we use direct neighbours of the classes that represent the correct answers.
Due to the limited nesting capabilties of SPARQL, which does not support loops but only subqueries that cannot access variables declared outside their scope, querying for distinct sets of 4 neighbours, where exactly one was connected over a certain property to a certain object, was not possible with our Virtuoso SPARQL endpoint initially.
We circumvented the timeout by calculating the neighbour-relation as a first step and uploading it to the endpoint.
%
%SNIK Quiz is freely available as an open source web application.
Because SNIK only contains the knowledge that the source textbooks describe, it does not contain the complete domain of Hospital Information Management.
As such, negative questions are problematic, as the given relationship could hold in the real world but not be described in the textbook source of the class.
The same problem concerns the distractors of positive questions.
So this problem cannot be avoided.
However, this is one of the reasons that we don't ask count questions like \enquote{How many functions is the CIO responsible for?}, which don't help much for learning anyways. % improve writing
Relationships could also hold implicitly through the subclass hierarchy.
For example, \aurl{bb}{ChiefInformationOfficer} is a subclass of \aurl{bb}{InformationManagementStaff}, which is responsible for \aurl{bb}{OperationalInformationManagement}.
It is unclear, whether the CIO is also responsible for operational information management.
An ongoing bachelor's thesis~\citep{snikquiz} is investigating different strategies of generating complex questions, answers and distrators.

@@

%\section{Acknowledgments}
%This work is supported by the DFG (German Research Foundation) under the Projects SNIK, grant no. 1605/7-1 and 1387/8-1, as well as HITO, grant no. WI 1605/11-1 and I3726-N31.
%We thank the publishers ... and ... for granting us permission to publish the subontologies based on the textbooks \citet{bb,ob,he} under an open license.
%\nocite{*} 
\todo{FJ: Hmmm, ziemlich selbstreferenziell. Brauchen wir da wirklich so viele Publikationen von uns? Welche anderen könnte man noch einbringen? Ich schaue auch mal, was mir so über den Weg läuft.}
%\bibliographystyle{ios1}
\bstctlcite{IEEE:BSTcontrol}
\bibliographystyle{IEEEtran}
\bibliography{paper,snik,relatedwork}
%\section{Notes to Reviewers}
%This paper includes and extends text and figures from:
%\citet{snikgraph}
%\todo{KH: Extending a poster should be allowed for a journal but maybe not for a conference. replace text and figures from the poster. should only be the snik graph chapter. use snik graph paper instead.}
%Update: All the text from the paper should now be commented out or properly referenced.
\end{document}
